---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
font-family: Arial;
}
h2 {
  color: #2c3e50;
  border-bottom: 2px solid #2c3e50;
}
```

## What's going on with this data?

This project analyzes survey data to see how many ads people see in a day, what content is recommended to them on youtube, what types of posts they interact with most, and how these variables all interact with one another

```{r}
library("tidyverse")
library("magick")
#data from google forms
logged_data <- read.csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRBjmMS7Ly3pxR9bQzqaYR5GFrZcPLBx9qzRlvoQDu3D-n4KjfHad4t_DWxZl3ekyjSkftm1u732XrK/pub?output=csv")

#renaming data 
latest_data <- logged_data %>%
  rename(
    ads_seen = 3,
    youtube_content = 4,
    interaction_type = 5
  )

#summary vals
mean_ads <- mean(latest_data$ads_seen, na.rm = TRUE)

min_ads <- min(latest_data$ads_seen, na.rm = TRUE)
max_ads <- max(latest_data$ads_seen, na.rm = TRUE)

num_responses <- nrow(latest_data)

#Graphs 1 & 2
#1 Youtube Rec.
ggplot(latest_data, aes(x = youtube_content)) +
  geom_bar(fill = "cyan") +
  labs(
    title = "YouTube Reccommended Content",
    x = "Content Type",
    y = "No. of Responses"
  ) +
  theme_minimal()

#2 UI types
ggplot(latest_data, aes(x = interaction_type)) +
  geom_bar(fill = "orange") +
  labs(
    title = "Most Common User Interaction Types",
    x = "Type of interaction",
    y = "No. of Responses "
  ) +
  theme_minimal() +
  #overlapping x axis text if not tilted
  theme(axis.text.x = element_text(angle = 35, hjust = 1))

summary(latest_data)

```

**Insights from the data:**

On average, responders reported seeing **`r round(mean_ads, 1)`** ads in the past 24 hours.

The highest number of ads seen by a single responder was **`r max_ads`** ads, showing some users either have very high exposure or were online for a very long time.

On the contrary, the lowest number of ads recorded was **`r min_ads`**, which shows just how varied the ad exposure can be between individuals

A total of **`r num_responses`** responses were collected for the analysis, providing a reasonable sample to infer general trends for user behaviour
